\section{Conclusion}
We have presented a method to optimize reversible logic synthesis using genetic algorithms. Additionally, we have detailed the implementation of a reversible logic synthesis framework which allowed us to implement the genetic algorithm method to a large extent. \\

Our algorithm shows promise, but it is by no means optimal: further investigation is required in order to ascertain its effectiveness due to discrepancies in quantum cost calculation between our framework and those presented in RevLib. \\

Future research in this area should address topics such as function-preserving mutation and crossover functions, as these were points of difficulty in our implementation. As our research focused more on the parallel implementation of a genetic algorithm, some more time should be spent on finding optimal cascade representations as well as on overall scalability. Currently, due to the nature of our approach, we require that a cascade's truth table be calculated before any quantum cost evaluation can take place. In practice, it would be far more efficient to utilize function-preserving transformations which would eliminate this requirement. \\

In conclusion, even though our algorithm delivered sub-optimal results, we were able to develop an effective and solid framework for future research on the optimization of large reversible cascades.

\begin{table}[H]
\begin{center}
    \begin{tabular}{l | l | l | l}
       Circuit            & Listed Cost & Our Calculated Cost & Best Generated  \\ 
                          & on RevLib   &                     & Circuit Cost    \\ \hline
     \verb!Max46_240!     & 5444                  & 15319               & 1281                        \\
     \verb!life_238!      & 6766                  & 11275               & 191                         \\
     \verb!f51m_233!      & 37400                 & 28303               & 32831                       \\
     \verb!alu-v0_27!     & 14                    & 14                  & 7                           \\
     \verb!decod24-v3_45! & 35                    & 35                  & 4                           \\
     \verb!gsym9!         & 206                   & 206                 & 154                         \\
     \verb!4gt11_83!      & 12                    & 12                  & 3                           \\
     \verb!gsym6!         & 72                    & 72                  & 66                          \\
     \verb!rd32_273!      & 116                   & 116                 & 92                          \\
     \verb!mod5adder_129! & 77                    & 77                  & 77                          \\
     \verb!hwb7_62!       & 2611                  & 2839                & 0                           \\
     \verb!urf4_187!      & 160020                & 160020              & N/A                          \\
     \verb!hwb8_116!      & 7015                  & 8341                & 0                           \\
     \verb!seq_314!       & 19362                 & N/A                  & N/A                          \\
     \verb!hwb9_121!      & 44665                 & N/A                  & N/A                          \\
    \end{tabular}
 \caption {Circuit Cost Comparisons}
\label{tab:CCC}
\end{center}
\end{table}