\section{Experimental Results}

We ran our genetic algorithm against 16 circuits found in the \url{revlib.org} circuit library. Table \ref{tab:CIR} shows the 
results of the trials for all 16 circuits. From these trials, we were able to generate results from 14 of the circuits. 9 of those 
trials also generated at least one circuit with an improved quantum cost when compared to the initialgit  circuit's {\verb .real } file which 
was downloaded from RevLib. The failure to generate any results for the circuits \verb!seq_314! and \verb!hwb9_121! is due to the 
time complexity of our fitness function and the extreme logical width of those circuits. \\

There were a number of circuits generated which showed a significant relative improvement in quantum cost over the original comparison 
circuit downloaded from RevLib (see Table 2). Upon doing a detailed comparison of our best circuits with their corresponding original circuit obtained from RevLib, we 
noticed a discrepency between our calculation of quantum cost for gates with more than four input lines and the RevLib calculations. We 
realized that our quantum cost calculation (which uses the quantum cost table found at \url{http://webhome.cs.uvic.ca/~dmaslov/definitions.html})
did not account for the garbage lines. This discrepency only exists in circuits with gates larger than 3 inputs, and all circuits that only consisted
of gates that were 3 input or smaller were accurately reported. We did not have the time to implement a revised quantum cost function which accounted 
for the garbage lines, however our results were self-consistent accross runs and it should only be a matter of revising our cost function and 
re-running our output circuits against the new cost function to compare the circuits with larger gates directly to the RevLib circuit. \\

\begin{table} [H]
\begin{center}
    \begin{tabular}{l | l | l | l | l | l}
    Circuit              & Attempted & Data        & Number of & \verb!%! of Runs  & Best Reported \\
                         &   Runs    & Generating  & Improved  & Generating an     & Quantum Cost  \\
                         &           & Runs        & Circuits  & Improved circuit  & Improvement \\ \hline
    \verb!Max46_240!     &  5000     & 5000        & 5000      & 100.00   & 14038       \\
    \verb!life_238!      &  5000     & 5000        & 4999      & 100.00   & 11084       \\
    \verb!f51m_233!      &  5000     & 60          & 60        & 100.00   & 4472        \\
    \verb!alu-v0_27!     &  1020     & 1020        & 904       & 88.63    & 7           \\
    \verb!decod24-v3_45! &  1020     & 1020        & 838       & 82.16    & 31          \\
    \verb!gsym9!         &  1040     & 1040        & 665       & 63.94    & 52          \\
    \verb!4gt11_83!      &  1020     & 1020        & 576       & 56.47    & 9           \\
    \verb!gsym6!         &  1020     & 1020        & 536       & 52.55    & 6           \\
    \verb!rd32_273!      &  1020     & 1020        & 526       & 51.57    & 92          \\
    \verb!mod5adder_129! &  5000     & 1277        & 0         & 0.00     & 0           \\
    \verb!hwb7_62!       &  5000     & 60          & 0         & 0.00     & 0           \\
    \verb!urf4_187!      &  1020     & 8           & 0         & 0.00     & N/A         \\
    \verb!hwb8_116!      &  5000     & 14          & 0         & 0.00     & 0           \\
    \verb!seq_314!       &  3060     & 0           & 0         & N/A      & N/A         \\
    \verb!hwb9_121!      &  1020     & 0           & 0         & N/A      & N/A         \\
    \end{tabular}
 \caption {Circuit Improvement Results}
\label{tab:CIR}
\end{center}
 \end{table}
